Effects of CHILDREN's programs

### 2020-02-25 paper.Rnw

@@

@@

<<ChanceEqualityRegressions, echo=FALSE, results='asis', message=FALSE>>=

>>>>

\begin{equation}
\label{Meals Grants Regression Model}
  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
\end{equation}

@@

Where: 
y: Health outcomes: lessIll, dietaryKnowledge,  appreciateHealthy
x: DGECriteria Number

@@

Where: 
y: Equal Opportunity proxies: selfworth, dayToDaySkills
x: Real Lunch grant, real Trips grant
<<ChanceEqualityRegressions, echo=FALSE, results='asis', message=FALSE>>=
